---
title: "adjustforinflation"
author: "Kyra Hendrickson"
date: "2022-11-4"
output: html_document
---
This file has contains a  for loop that takes:
a vector of $prices, a vector of years those prices were from and outputs a vector of adjusted $prices for inflation 
for a specified country and date. 
 * For loop on line 76. 
 *There's an example of how to use it on line 41.
 * Line 97: Using this loop for budget and revenue on movies_filtered, don't have a vector of years yet though.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Imports
```{r}
library(tidyverse)
library(readr)
library(knitr)
library(kableExtra)
library(caret)
library(klaR)
```

```{r}
require("quantmod");require("PerformanceAnalytics");require("Quandl")
```

Download data
```{r}
movies_filtered <- read_csv('movies_filtered2.csv', col_names =c('title','genres','original_language','production_companies','budget','revenue','runtime','vote_average','vote_count','credits'), trim_ws = TRUE, show_col_types = FALSE)
```


    print row 62 below. Using 61 in argument because the code counts the header as the first row.
```{r}
movies_filtered[1:10,]
```

===================================================================================================================
example from https://app.datacamp.com/workspace/preview?_tag=rdocs&rdocsPath=packages%2FpriceR%2Fversions%2F0.1.6%2Ftopics%2Fadjust_for_inflation&utm_source=r-docs&utm_medium=docs&utm_term=adjust_for_inflation&utm_content=run_example_in_workspace

```{r}
if(!require('PriceR')){
  install.packages('priceR')
  library('priceR')
}
```
from australia, convert $100 from 2005 into 2017 dollars
```{r}
country <- "AU"
inflation_dataframe <- retrieve_inflation_data(country)
countries_dataframe <- show_countries() 
```
```{r}
adjust_for_inflation(100, 2005, country, to_date = 2017,
inflation_dataframe = inflation_dataframe,
countries_dataframe = countries_dataframe)

adjust_for_inflation(200, 2005, country, to_date = 2017,
inflation_dataframe = inflation_dataframe,
countries_dataframe = countries_dataframe)

adjust_for_inflation(300, 2005, country, to_date = 2017,
inflation_dataframe = inflation_dataframe,
countries_dataframe = countries_dataframe)

```

```{r}
vectorofprices <- c(100,200,300)
fromdates <- c(2005,2005,2005)
todates <- c(2017,2017,2017)
```

```{r}
# # run a for loop that outputs a vector of adjusted prices
adjusted_prices <- vector(mode="numeric")
for (i in 1:length(vectorofprices)){
  new_prices <- adjust_for_inflation(vectorofprices[i], fromdates[i], country, todates[i],
    inflation_dataframe = inflation_dataframe,
    countries_dataframe = countries_dataframe)
  adjusted_prices <- append(adjusted_prices, new_prices)
}
```

```{r}
print(adjusted_prices)
```

============================================================================
back to movies_filtered data

```{r}
# set country
country <- "US"
inflation_dataframe <- retrieve_inflation_data(country)
countries_dataframe <- show_countries() 

# get budget and revenue vector 
budgets <- movies_filtered[5]
revenue <- movies_filtered[6]
to_date = 2022

# commented out down here is how to adjust budget for inflation, just switch budget to revenue for revenue adjustment"

"
from_dates <- movies_filtered[NA atm]
adjusted_prices <- vector(mode="numeric")
for (i in 1:length(budgets)){
  new_prices <- adjust_for_inflation(budgets[i], from_dates[i], country, to_date,
    inflation_dataframe = inflation_dataframe,
    countries_dataframe = countries_dataframe)
  adjusted_prices <- append(adjusted_prices, new_prices)
}"
```


```{r}

```

