---
title: "preprocess"
author: "Kyra Hendrickson"
date: "2022-10-24"
output: html_document
---
This file pre-processes our data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Stage I: Preprocess

1. Download movies data (10/24 version latest movie is Black Adam):
```{r}
originaldata <- read.csv("C:\\Users\\Kyra\\OneDrive\\Documents\\CS5232project\\movies.csv")
```

2. Drop irrelevant columns
```{r}
df = subset(originaldata, select = -c(id, overview, tagline, keywords, poster_path, backdrop_path, recommendations) )
```

3. Get rid of movies that haven't been released according to Status column. For example: "In Production" movies (https://www.programmingr.com/count-occurrences-in-column/)
```{r}
table(df$status)
```

4. Impute NAs with MICE package
```{r}

```

5. Shuffle df by rows (follow https://www.geeksforgeeks.org/how-to-shuffle-a-dataframe-in-r-by-rows/) save as "df"
```{r}

```

6. Subset 10% of data, call it "testSet" and save as a csv file, also save the other 90% of shuffled data in a separate file and call it "trainingSet"

** for SVM we can use the trainingSet to train with k-fold and go an extra step and do k-fold with testSet for the final model if we like (or just use only trainingSet)
```{r}

```

Stage II: Linear Regression in a separate file predicting revenue

Task 1: Decide what a successful revenue is
For example:
 <1 mil = not successful
1 mil<revenue<10 = moderately successful
10 mil> = very successful

Task 2: build model

Stage III:
Implementing SVM alg (https://www.youtube.com/watch?v=RKZoJVMr6CU demo starts at 13:39) and the other algs in seperate files

