---
title: "svm_Budget_Studio"
author: "Kyra Hendrickson"
date: "2022-11-22"
output: html_document
---
determine what parameters your hyperplane needs to separate data in terms of: 
ratio <= 1
ratio > 1
Answers which budget and studio company combination will make money by classifying data into ratio<=1 and ratio>1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# libraries
library(tidyverse)
library(readr)
library(DataExplorer)
library(plotly)
library(caret)
library(ggplot2)
library(dplyr)

install.packages("e1071")
library(e1071)

library(MASS) 
library(reshape2) 
```
Prepping data for svm 
```{r}
# download test and training data
names = c('budget','revenue','runtime','vote_average','vote_count','en','hu','fr','ru','es','Action','Comedy','Drama','Romance','Thriller','Dwayne.Johnson','Samuel.L..Jackson','Tom.Hanks','Johnny.Depp','Harrison.Ford','Denzel.Washington',	'Morgan.Freeman',	'Robert.De.Niro',	'Bruce.Willis',	'Meryl.Streep',	'Robert.Downey.Jr.',	'Tom.Cruise',	'Warner.Bros',	'Universal',	'X20th.Century.Fox',	'Paramount',	'Columbia' ,	'Pixar',	'Marvel', 	'Walt.Disney')

movie_train <- read_csv('movie_train.csv', col_names=names, trim_ws = TRUE, show_col_types = FALSE)[-c(1), ]
movie_test <- read_csv('movie_test.csv', col_names=names, trim_ws = TRUE, show_col_types = FALSE)[-c(1), ]

```

```{r}
## Create indicator column

# create net revenue col
movie_train$budget <- as.numeric(movie_train$budget)
movie_train$revenue <- as.numeric(movie_train$revenue)
movie_train$net.revenue <- (movie_train$revenue - movie_train$budget)

movie_test$budget <- as.numeric(movie_test$budget)
movie_test$revenue <- as.numeric(movie_test$revenue)
movie_test$net.revenue <- (movie_test$revenue - movie_test$budget)

# create revenue/budget ratio col, this is our indicator variable
movie_train$ratio <- abs(movie_train$net.revenue/movie_train$budget)
movie_test$ratio <- abs(movie_test$net.revenue/movie_test$budget)

# create a new col as indicator col, need to seperate ratio into <1 and >1
movie_train$ratio_indicator<-factor(ifelse(movie_train$ratio<1,"No.Profit","Profit"))
movie_test$ratio_indicator<-factor(ifelse(movie_test$ratio<1,"No.Profit","Profit"))
```


```{r}
## Turn studio into numerical attribute, get one column 

# studios into numerical attribute, melt_test is the new testing data
melt_train <- melt(movie_train, id = c('budget','revenue','runtime','vote_average','vote_count','en','hu','fr','ru','es','Action','Comedy','Drama','Romance','Thriller','Dwayne.Johnson','Samuel.L..Jackson','Tom.Hanks','Johnny.Depp','Harrison.Ford','Denzel.Washington',	'Morgan.Freeman',	'Robert.De.Niro',	'Bruce.Willis',	'Meryl.Streep',	'Robert.Downey.Jr.',	'Tom.Cruise','net.revenue','ratio','ratio_indicator')) 

melt_train = melt_train[melt_train$value ==TRUE, ] # takes out duplicates by getting rid of all the FALSE values
names(melt_train)[31] = "studio" # rename 31st col studio

studio_vector_train <-unclass(melt_train$studio)
studio_vector_train

melt_train$studio_unclass <- studio_vector_train

```

```{r}
## same process for testing set 

# studios into numerical attribute, melt_test is the new testing data
melt_test <- melt(movie_test, id = c('budget','revenue','runtime','vote_average','vote_count','en','hu','fr','ru','es','Action','Comedy','Drama','Romance','Thriller','Dwayne.Johnson','Samuel.L..Jackson','Tom.Hanks','Johnny.Depp','Harrison.Ford','Denzel.Washington',	'Morgan.Freeman',	'Robert.De.Niro',	'Bruce.Willis',	'Meryl.Streep',	'Robert.Downey.Jr.',	'Tom.Cruise','net.revenue','ratio','ratio_indicator')) 

melt_test = melt_test[melt_test$value ==TRUE, ]

names(melt_test)[31] = "studio"

studio_vector_test <-unclass(melt_test$studio)
studio_vector_test

melt_test$studio_unclass <- studio_vector_test
```
notes: 
studio_unclass -> col of numbers 1-8 corresponding to studio:
  [1] "Warner.Bros"       "Universal"         "X20th.Century.Fox" "Paramount"        
  [5] "Columbia"          "Pixar"             "Marvel"            "Walt.Disney"  

```{r}
# final svm-ready training and test set
cols = c("studio_unclass","budget","ratio_indicator")
budgetStudio_trian = melt_train[cols]
budgetStudio_test = melt_test[cols]
```


```{r}
# plot training data
yp_train = melt_train$studio_unclass[melt_train$ratio_indicator =="Profit"] # profit y values
xp_train = melt_train$budget[melt_train$ratio_indicator =="Profit"] # profit x-values

ynp_train = melt_train$studio_unclass[melt_train$ratio_indicator =="No.Profit"] # no profit y values
xnp_train = melt_train$budget[melt_train$ratio_indicator =="No.Profit"] # no profit x-values

plot(xp_train,yp_train,main="Studio vs. Budget",col="green",xlab = "Budget",ylab = "Studio")
points(xnp_train,ynp_train,col="red")
legend(x = "topright", lty = c(6,6), text.font = 2, 
       col= c("green","red"),text.col = "blue", 
       legend=c("Profit", "No Profit"))
```
```{r}
# plot test data
yp_test = melt_test$studio_unclass[melt_test$ratio_indicator =="Profit"] # profit y values
xp_test = melt_test$budget[melt_test$ratio_indicator =="Profit"] # profit x-values

ynp_test = melt_test$studio_unclass[melt_test$ratio_indicator =="No.Profit"] # no profit y values
xnp_test = melt_test$budget[melt_test$ratio_indicator =="No.Profit"] # no profit x-values

plot(xp_test,yp_test,main="Studio vs. Budget",col="green",xlab = "Budget",ylab = "Studio")
points(xnp_test,ynp_test,col="red")
legend(x = "topright", lty = c(6,6), text.font = 2, 
       col= c("green","red"),text.col = "blue", 
       legend=c("Profit", "No Profit"))
```

1-Warner.Bros, 2-Universal,  3-X20th.Century.Fox,  4-Paramount,  5-Columbia,  6-Pixar,  7-Marvel, 8-Walt.Disney



```{r}
# final svm-ready training set
cols = c("studio_unclass","budget","ratio_indicator")
trainData = melt_train[cols]
testData = melt_test[cols]
```



Create svm models. 
Three experiments: polynomial, sigmoid, and radial
1. Polynomial kernel 
```{r}
polymodel <- svm(formula = ratio_indicator ~.,
              data = trainData,
              kernel = 'polynomial',
              gamma=1, 
              cost =1 
              )
summary(polymodel)
```

evaluating model
```{r}
# visualize results
plot(polymodel,trainData)
# Predicting using the test set
ypoly_pred = predict(polymodel,newdata = testData[-3])
cm = table(testData[,3], ypoly_pred)
tn = cm[1]
fn = cm[2]
fp = cm[3]
tp = cm[4]
n = sum(cm)
accuracy = (tp + tn)/n
precision = tp/(fp + tp)

print(cm)
sprintf('accuracy: %s ', accuracy)
sprintf('precision: %s ', precision)
```

2. Sigmoid kernel
```{r}
sigmodel <- svm(formula = ratio_indicator ~.,
              data = trainData,
              kernel = 'sigmoid',
              gamma=1, 
              cost =1 
              )
summary(sigmodel)
```

```{r}
# visualize results
plot(sigmodel,trainData)
# Evaluate model
yradial_pred = predict(sigmodel,newdata = testData[-3])
cm = table(testData[,3], y_pred)
tn = cm[1]
fn = cm[2]
fp = cm[3]
tp = cm[4]
n = sum(cm)
accuracy = (tp + tn)/n
precision = tp/(fp + tp)

print(cm)
sprintf('accuracy: %s ', accuracy)
sprintf('precision: %s ', precision)
```

3. Radial kernel 
```{r}
radialmodel <- svm(formula = ratio_indicator ~.,
              data = trainData,
              kernel = 'radial',
              gamma=1, 
              cost =5 
              )
summary(radialmodel)
```


```{r}
# visualize results
plot(radialmodel,trainData)
# Evaluate model
yradial_pred = predict(radialmodel,newdata = testData[-3])
cm = table(testData[,3], y_pred)
tn = cm[1]
fn = cm[2]
fp = cm[3]
tp = cm[4]
n = sum(cm)
accuracy = (tp + tn)/n
precision = tp/(fp + tp)

print(cm)
sprintf('accuracy: %s ', accuracy)
sprintf('precision: %s ', precision)
```
tuning parameters from each experiment

